A Detection of the Environmental Dependence of the Stellar Halos of Massive Central Galaxies

### 2017-03-14 draft/ms_v4.tex
New draft

% Version 0; preprint format; Written by SH
% Version 1; emulateapj format; Edited by SH and AL
% Version 2; emulateapj format; Edited by SH and AL
% Version 3; emulateapj format; Edited AL
% Version 4; emulateapj format; Edited SH
% Version 5; MNRAS format; Edited SH

\documentclass[a4paper,fleqn,usenatbib]{mnras}

% Packages
%\usepackage{deluxetable}
%\usepackage{apjfonts}
\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb, amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{float}
\usepackage[usenames, dvipsnames]{color}

% Package Settings
\hypersetup{colorlinks=true,
            citecolor=cyan,
            linkcolor=cyan,
            filecolor=magenta,      
            urlcolor=cyan}
\urlstyle{same}

% Figure extention
\DeclareGraphicsExtensions{.pdf,.png,.jpg}

@@

\def\logminn{{$\log (M_{\star,10\mathrm{kpc}}/M_{\odot})$}}
\def\logmtot{{$\log (M_{\star,100\mathrm{kpc}}/M_{\odot})$}}
\def\logmout{{$\log (M_{\star,150\mathrm{kpc}}/M_{\odot})$}}
\def\logmmax{{$\log (M_{\star,\mathrm{Max}}/M_{\odot})$}}
\def\logmgama{{$\log (M_{\star,\mathrm{GAMA}}/M_{\odot})$}}
\def\logmcmodel{{$\log (M_{\star,\mathrm{cModel}}/M_{\odot})$}}

@@

@@

\title[Structure and Halo of Massive Galaxies]{A Detection of the Environmental 
       Dependence of the Stellar Halos of Massive Central Galaxies}

\author[S. Huang et al.]{Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        HSC collaboration$^{3}$   
        \\ \\
        % List of institutions
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$Another Department, Different Institution, Street Address, City Postal 
              Code, Country
        }

\date{Accepted XXX. Received YYY; in original form ZZZ}        
\pubyear{2017}

%        \author{Song Huang\altaffilmark{1} 
%        Alexie Leauthaud\altaffilmark{1}, 
%        Kevin Bundy\altaffilmark{1},
%        Michael Strauss\altaffilmark{2},
%        Yen-Ting Lin\altaffilmark{3},
%        Rachel Mandelbaum\altaffilmark{4}
%        }
%\altaffiltext{2}{Princeton University Observatory, 
%    Peyton Hall, Princeton, NJ 08544, USA}
%\altaffiltext{3}{Institute of Astronomy and Astrophysics, Academia Sinica, 
%    P.O.~Box 23--141, Taipei 10617, Taiwan}
%\altaffiltext{4}{Carnegie-Mellon University \todo{correct affiliation here}}

\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}

@@

\end{abstract}

\begin{keywords}
    galaxies: elliptical and lenticular, cD --
    galaxies: formation --
    galaxies: photometry -- 
    galaxies: structure -- 
    galaxies: surveys}
\end{keywords}

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_sdss_compare}
        \caption{
            A comparison between the imaging quality of SDSS and HSC Wide for a sample 
        	of nearby massive elliptical galaxies at $0.2 < z < 0.5$.  
            These images are generated using $gri$ band images with an arcsinh stretch 
            \citep{Lupton2004}. 
            The HSC \texttt{WIDE} layer is $3.0$-$4.0$ magnitudes deeper than SDSS 
            which is critical to map the outskirts of ETGs out to large radii.
            }
        \label{fig:sdss_compare}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
      \caption{
          Three-color images for a subsample of massive galaxies at $z\sim 0.4$, and 
          with similar values for their \mstar{} within a 10 kpc aperture 
          (the dash-line circle on top-left figure indicates the scale of 10 kpc;
          $11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
          Galaxies are rank-ordered from top to bottom and from left to right by 
          their \mstar{} within 100 kpc aperture which varies from $10^{11.2} M_{\odot}$ 
          to $10^{11.7} M_{\odot}$. 
          At fixed "inner" mass ($M_{\star,10}$), massive galaxies display significant
          diversity in their outer profiles. 
          Red boxes indicate galaxies in halos more massive than 
          $\sim 10^{14.0} M_{\odot}$. 
          }
      \label{fig:m100_m10_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    Massive galaxies are unique laboratories to study both cosmology and galaxy 
    formation. 
    Although the hierarchical growth scenario under the $\Lambda$-CDM cosmology 
    is a solid theoretical background (e.g. \citealt{Baugh1996, DeLucia2006}, 
    plenty important questions regarding the star-formation history, mass assembly 
    process, and structural evolution of these massive galaxies remain open. 
    Thanks to the advances in observations and numerical simulations, the newly 
    developed ``two-phase'' formation scenario (e.g. \citealt{Oser2010, Oser2012}) 
    becomes the most promising theory that can reasonably explain different 
    observations of massive galaxies. 
    Under this picture, the highly dissipative processes at high-$z$ (e.g cold 
    accretion, gas-rich merger; e.g. \citealt{Hopkins2008, Dekel2009}) induce 
    intense starburst, and quickly form the massive progenitors of $z\sim 0$ massive 
    early-type galaxies (ETGs).     
    Later, certain physical mechanism (e.g. AGN feedback; e.g. \citealt{Sijacki2007,
    Fabian2012}) 
    efficiently quenched the on-going star formation so that a large fraction of 
    these massive progenitors become quiescent at $z>1$ (e.g. \citealt{Bezanson2009,
    Kriek2016}). 
    At the same stellar mass (\mstar{}), these so-called ``red nuggets'' 
    (e.g. \citealt{Damjanov2009}) have smaller effective radius 
    ($R_{\mathrm{e}}$; \citealt{Trujillo2006, vanDokkum2008, Cimatti2008}), 
    slightly higher central velocity dispersion and stellar mass density 
    (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like morphology 
    (e.g. \citealt{vanderWel2011}) than their local descendants 
    (e.g. \citealt{Bezanson2009, vanDokkum2010}). 
    Later, the second phase of evolution is driven by non-dissipative processes 
    like dry mergers with other galaxies (e.g. \citealt{Naab2006, Khochfar2006}). 
    According to the ``two-phase'' scenario, minor mergers make dominated 
    contribution during this period as they help explain the significant increase
    of $R_{\mathrm{e}}$ (e.g. \citealt{Newman2012, vdWel2014}) and accumulation of 
    outer stellar halo (e.g.  \citealt{Szomoru2012, Patel2013}).

    Despite the great success, it also raises new questions. 
    Under the $\Lambda$-CDM cosmology, the formation of galaxy is intrinsically 
    tied to the growth of the host dark matter halo 
    (e.g. \citealt{Leauthaud2012, Behroozi2013}).
    Massive ETGs living in the center of more massive halos should experience 
    different mass assembly history and undergo different merging events comparing 
    to the ones from smaller halos. 
    Therefore, it is reasonable to expect that the structures of massive galaxies
    depend on the ``environment''\footnote{Although there are different 
    observational definition of environment, we use the term ``environment'' and 
    halo mass interchangeably in this work.}.

    As one of the most important structural parameters, the $R_{\mathrm{e}}$ of 
    massive ETGs follows a tight and steep relation with the \mstar{} 
    (e.g. \citealt{Shen2003, Guo2009}). 
    Models based on the ``two-phase'' formation scenario naturally predict that 
    such mass--size relation should show environmental dependence, and 
    $R_{\mathrm{e}}$ of massive ETGs in more massive halos should be larger 
    than the ones in less massive halos at fixed \mstar{} 
    (e.g. \citealt{Shankar2013, Shankar2014}). 
    Interestingly, while hints of such dependence have been spotted at high-$z$ 
    (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but also see 
    \citealt{Rettura2010}), solid evidence of it at low-$z$ is still absence 
    (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}).
    This confusing result becomes a challenge to the hierarchical growth model 
    of massive galaxies. 
    On the observational side, both the depth of the images and the photometric 
    method contribute to this problem. 
    The steep inner \mden{} profiles, extremely extended stellar envelopes, 
    and other structural details make it very difficult to accurately define and 
    measure the \mstar{} and $R_{\mathrm{e}}$ of massive ETGs 
    (e.g. \citealt{Bernardi2013, DSouza2014}).

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
        \caption{
            Left: example of the 1-D surface brightness and ellipticity profile 
            for a massive galaxy at $z=0.23$ in the $i$-band using \texttt{Ellipse}. 
            In this work, we always show the radial profile using a $R^{1/4}$ scaling 
            on the x-axis. 
            By using this scale, the de Vaucouleurs profile will appear as a straight 
            line on this figure. 
            The dash-line shows the surface brightness profile after correcting the 
            background. 
            We also plot the relative brightness profile of the PSF model normalized 
            at the central surface brightness of the galaxy to highlight the region 
            affected by seeing. 
            The grey shaded region highlights the region most affect by seeing 
            ($r<3$ kpc).
            On the top panel, the dash line shows the ellipticity used for the final 
            isophote. 
            Right: the masked $i$-band image of this galaxy with the isophotes 
            extracted by \texttt{Ellipse}. 
            The thick dotted line highlights the isophote with 
            $\mu_{i}\sim 28.5$~\sb.
            }
        \label{fig:ellipse}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_smf_new}
      \caption{
          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
          On average, \mcmodel{} underestimates the total stellar mass of massive 
          galaxies by 0.1 dex while the difference can exceed 0.2 dex in some cases.
          Vertical histograms indicate the mass difference for galaxies with
          $11.6<$\logmtot{}$<11.9$. 
          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
          function. 
          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
          of the total luminosity whereas solid lines correspond to the SMF computed
          using the total luminosity from our 1-D profile. 
          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
          living in halos larger than $\log (M_{200m}/M_{\odot}) > 14.2$ (red lines).
          }
      \label{fig:smf1}
  \end{figure*}

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/average_mass_profiles_fsps1_A}
      \caption{
          \textbf{Left}: Median \mden{} profiles of galaxies in different \mtot{} bins:
      	  [11.4, 11.6] (short-dashed line), [11.6, 11.8] (solid line), and 
      	  [11.8, 12.0] (long-dashed line). 
      	  Here we combine the \rbcg{} and \nbcg{} samples, and we also show a random 
      	  subset of individual profiles in the background.
      	  The shaded region highlights the region that could be affected by PSF.
          Two vertical lines label the radius of 10 kpc (thin, dotted line) and
          100 kpc (thick, dash line). ~~~ 
          \textbf{Right}: comparison between the average \mden{} profiles with the ones 
          from previous observations and simulations, including: 
          1) average profile of massive elliptical galaxies at $z\sim 0$ from 
          \citet[][Cyan, solid]{Huang2013a}; 
          2) average profile of massive galaxies at $0.25 \leq z < 0.50$ observed by 
          \textit{HST} from \citet[][Red, long-dashed]{Patel2013} ;
          3) average radial stellar distributions in massive halos using simulation and 
          particle tagging method (\citealt{Cooper13}; Purple, short-dashed).
          }
      \label{fig:avg_prof}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
      \caption{
          Comparison of the \mden{} profiles for \mtot{}-matched 
          ($11.6<$\logmtot{}$<11.9$) and \minn{}-matched ($11.2<$\logminn{}$<11.6$) 
          samples of \rbcg{} (orange to red) and \nbcg{} (grey to black) galaxies.~~
          \textbf{Left} shows the results for the \mtot{}-matched samples.
          For details of the matching process, please see Appendix~\ref{app:match}.  
          On its upper panel, we show the \mden{} profile of each galaxy using very light 
          color in the background.  
          We highlight the median profile and its corresponding uncertainties using thick 
          solid line with darker color and shaded region. 
          Other formats are the same with Fig~\ref{fig:avg_prof}.
          Meanwhile, we highlight the difference between the median profiles and its 
          uncertainty on the bottom panel (brown solid line and shaded region).
          To test the significance of the differential profile, we perform statistical
          tests by comparing the median profiles of two random groups that are drawn 
          from the mixed sample, and have the same sizes with the matched \rbcg{} and
          \nbcg{} ones.
          Repeating this process many times, the median of these random differential 
          profiles (black solid line), the 1-$\sigma$ (dark-grey shaded region) and 
          3-$\sigma$ (light-grey shaded region) uncertainties are shown on the bottom 
          panel as well. 
          A darker vertical dash-line highlights the 100 kpc radius.~~
          \textbf{Right} shows the results for the \minn{}-matched samples. 
          The format is exactly the same with the left one, except that the darker 
          vertical dash-line now highlights the 10 kpc radius.
          }
      \label{fig:prof_1} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    As mentioned above, different methods lead to different estimates of ``total'' 
    \mstar{} and impacts important statistics like the stellar mass function 
    (e.g. \citealt{Bernardi2013, DSouza2014, DSouza2015, Bernardi2016a}).
    We highlight this in the left panel of Fig~\ref{fig:smf1} by plotting 
    the \mtot{} from 1-D analysis with the differences between \mtot{} and \mcmodel{}.
    Apparently, our careful 1-D approach recovers more flux in massive galaxies 
    than the \texttt{cModel} method. 
    More importantly, the average difference steadily increases with \mtot{}. 
    At \logms$>11.5$, the difference is often larger than 0.2 dex.  
    This difference relates to the intrinsic limitation of the \texttt{cModel} 
    method and also reflects the fact that more massive ETGs tend to have more 
    extended stellar mass distributions (e.g. \citealt{Graham2003}).

    Such mass-dependent difference will clearly result in difference of the SMF, 
    especially at the very high-mass end where the slope is quite uncertain under
    current constraints (e.g. \citealt{Bernardi2016}).
    Although the careful evaluation of the SMF is beyond the scope of this work, 
    we still highlight the impacts of different definitions of ``total \mstar{}''
    on the volume density distributions of both samples (Fig~\ref{fig:smf1}, 
    right panel).  
    Generally speaking, the use of \mtot{} from 1-D analysis instead of the
    \mcmodel{} shifts the distributions toward the higher-mass end, and slightly 
    modifies the slope.
    This impact is more obvious for the \rbcg{} samples.
    For studies about the SMF or other aspects of galaxy evolution based on 
    \cmodel{}-like photometry or shallower images, these impacts should be 
    taken into consideration.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_discussion_2}
      \caption{
          Comparisons of the radial profiles of ellipticity and optical colors 
      	  for \mtot{}-matched (\textbf{left figure}) and \minn{}-matched 
      	  (\textbf{right figure}) of \rbcg{} (orange-red) and \nbcg{} (grey-black) samples. 
          The formats are very similar to the figure for \mden{} profile 
          (e.g. right figure of Fig~\ref{fig:prof_1}). 
          On each side, from top to bottom, we show the elliptical profile, and the 
          color profile using $g-r$ and $g-i$ color. 
          Since the individual profile of these properties has very large uncertain in the 
          outskirt, we block the region at large radii where we think the median profiles 
          are still unreliable using a dark, shaded box.
          We also compare these results with previous results based on SDSS images. 
          They are: 
          1) Ellipticity profile of the stacked image of a large sample of red galaxies at 
          $z\sim 0.4$ from \citet{Tal2011} with PSF correction 
          (solid blue line on top panel); 
          2) Ellipticity and $g-r$ color profiles from stacking analysis of nearby massive 
          galaxies with high concentration index ($C>2.6$) in \citet[][blue dash lines 
          on the top and middle panels]{DSouza2014}; 
          3) average $g-r$ and $g-i$ color profiles for a large sample of nearby 
          elliptical galaxies in \citet[][blue, solid lines on the middle and bottom 
          panels]{LaBarbera2010}.
          }
      \label{fig:ell_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%\acknowledgements
\section*{Acknowledgements}

@@

\bibliographystyle{mnras}
\bibliography{redbcg}

>>>>

% Version 0; preprint format; Written by SH
% Version 1; emulateapj format; Edited by SH and AL
% Version 2; emulateapj format; Edited by SH and AL
% Version 3; emulateapj format; Edited AL
% Version 4; emulateapj format; Edited SH

%\documentclass[twocolumn]{aastex6}
\documentclass{emulateapj}

% Packages
%\usepackage{emulateapj5}
\usepackage{apjfonts}
\usepackage{amssymb, amsmath}
\usepackage{graphicx}
\usepackage{CJK}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{float}
\usepackage[usenames, dvipsnames]{color}

% Package Settings
\bibliographystyle{apj}
\hypersetup{colorlinks=true,
            citecolor=cyan,
            linkcolor=cyan,
            filecolor=magenta,      
            urlcolor=cyan}
\urlstyle{same}

% Figure extention
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
%\input psFig~tex

@@

\def\logminn{{$\log (M_{\star,10\mathrm{kpc}}/M_{\odot})$}}
\def\logmtot{{$\log (M_{\star,100\mathrm{kpc}}/M_{\odot})$}}
\def\logmout{{$\log (M_{\star,150\mathrm{kpc}}/M_{\odot})$}}
\def\logmmax{{$\log (M_{\star,\mathrm{Max}}/M_{\odot})$}}
\def\logmgama{{$\log (M_{\star,mathrm{GAMA}}/M_{\odot})$}}
\def\logmcmodel{{$\log (M_{\star,mathrm{cModel}}/M_{\odot})$}}

@@

\shorttitle{ENVIRONMENT DEPENDENCE OF MASS-SIZE RELATION}
\shortauthors{HUANG ET AL.}
\slugcomment{Draft version 2}

\begin{CJK*}{UTF8}{gbsn}

@@

\title{A Detection of the Environmental Dependence of the Stellar Halos of 
       Massive Central Galaxies}

\author{Song Huang (黄崧)\altaffilmark{1}, 
        HSC collaboration\altaffilmark{1}}   
%        \author{Song Huang (黄崧)\altaffilmark{1} 
%        Alexie Leauthaud\altaffilmark{1}, 
%        Kevin Bundy\altaffilmark{1},
%        Michael Strauss\altaffilmark{2},
%        Yen-Ting Lin\altaffilmark{3},
%        Rachel Mandelbaum\altaffilmark{4}
%        }

\email{song.huang@ipmu.jp}

\date{}

\altaffiltext{1}{Kavli Institute for the Physics and Mathematics of the 
    Universe, The University of Tokyo Institutes for Advanced Study, 
    the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan}
%\altaffiltext{2}{Princeton University Observatory, 
%    Peyton Hall, Princeton, NJ 08544, USA}
%\altaffiltext{3}{Institute of Astronomy and Astrophysics, Academia Sinica, 
%    P.O.~Box 23--141, Taipei 10617, Taiwan}
%\altaffiltext{4}{Carnegie-Mellon University \todo{correct affiliation here}}

@@

\end{abstract}
\keywords{galaxies: elliptical and lenticular, cD --- 
          galaxies: formation --- 
          galaxies: photometry --- 
          galaxies: structure --- 
          galaxies: surveys}

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}[t!]
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_sdss_compare}
        \caption{
            A comparison between the imaging quality of SDSS and HSC Wide for a sample 
        	of nearby massive elliptical galaxies at $0.2 < z < 0.5$.  
            These images are generated using $gri$ band images with an arcsinh stretch 
            \citep{Lupton2004}. 
            The HSC \texttt{WIDE} layer is $3.0$-$4.0$ magnitudes deeper than SDSS 
            which is critical to map the outskirts of ETGs out to large radii.
            }
        \label{fig:sdss_compare}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[t!]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
      \caption{
          Three-color images for a subsample of massive galaxies at $z\sim 0.4$, and 
          with similar values for their \mstar{} within a 10 kpc aperture 
          (the dash-line circle on top-left figure indicates the scale of 10 kpc;
          $11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
          Galaxies are rank-ordered from top to bottom and from left to right by 
          their \mstar{} within 100 kpc aperture which varies from $10^{11.2} M_{\odot}$ 
          to $10^{11.7} M_{\odot}$. 
          At fixed "inner" mass ($M_{\star,10}$), massive galaxies display significant
          diversity in their outer profiles. 
          Red boxes indicate galaxies in halos more massive than 
          $\sim 10^{14.0} M_{\odot}$. 
          }
      \label{fig:m100_m10_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    Massive galaxies are unique laboratories to study both cosmology and galaxy 
    formation. 
    Although the hierarchical growth scenario under the $\Lambda$-CDM cosmology 
    is a solid theoretical background (e.g. \addref{}, plenty important questions 
    regarding the star-formation history, mass assembly process, and structural 
    evolution of these massive galaxies remain open. 
    Thanks to the advances in observations and numerical simulations, the newly 
    developed ``two-phase'' formation scenario (e.g. \citealt{Oser2010, Oser2012}) 
    becomes the most promising theory that can reasonably explain different 
    observations of massive galaxies. 
    Under this picture, the highly dissipative processes at high-$z$ (e.g cold 
    accretion, gas-rich merger; e.g. \addref{}) induce intense starburst, and 
    quickly form the massive progenitors of $z\sim 0$ massive early-type galaxies 
    (ETGs). 
    Later, certain physical mechanism (e.g. AGN feedback; e.g. \addref{}) 
    efficiently quenched the on-going star formation so that a large fraction of 
    these massive progenitors become quiescent at $z>1$ (e.g. \addref{}). 
    At the same stellar mass (\mstar{}), these so-called ``red nuggets'' 
    (e.g. \addref{}) have smaller effective radius ($R_{\mathrm{e}}$; \addref{}), 
    slightly higher central velocity dispersion and stellar mass density 
    (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like morphology 
    (e.g. \addref{}) than their local descendants (e.g. \citealt{Bezanson2009,
    vanDokkum2010}). 
    Later, the second phase of evolution is driven by non-dissipative processes 
    like dry mergers with other galaxies (e.g. \addref{}). 
    According to the ``two-phase'' scenario, minor mergers make dominated 
    contribution during this period as they help explain the significant increase
    of $R_{\mathrm{e}}$ (e.g. \citealt{Newman2012, vdWel2014}) and accumulation of 
    outer stellar halo (e.g.  \citealt{Szomoru2012, Patel2013}).

    Despite the great success, it also raises new questions. 
    Under the $\Lambda$-CDM cosmology, the formation of galaxy is intrinsically 
    tied to the growth of the host dark matter halo (e.g. \addref{}).
    Massive ETGs living in the center of more massive halos should experience 
    different mass assembly history and undergo different merging events comparing 
    to the ones from smaller halos. 
    Therefore, it is reasonable to expect that the structures of massive galaxies
    depend on the ``environment''\footnote{Although there are different 
    observational definition of environment, we use the term ``environment'' and 
    halo mass interchangeably in this work.}.

    As one of the most important structural parameters, the $R_{\mathrm{e}}$ of 
    massive ETGs follows a tight and steep relation with the \mstar{} 
    (e.g. \addref{}). 
    Models based on the ``two-phase'' formation scenario naturally predict that 
    such mass--size relation should show environmental dependence, and 
    $R_{\mathrm{e}}$ of massive ETGs in more massive halos should be larger 
    than the ones in less massive halos at fixed \mstar{} (e.g. \addref{}). 
    %% Shankar 2013; 2014
    Interestingly, while hints of such dependence have been spotted at high-$z$ 
    (e.g. \citealt{Papovich2012, Delaye2014}; but also see \addref{}), solid 
    evidence of it at low-$z$ is still absence (e.g. \citealt{Nair2010, HCompany13};
    but also see \addref{}).
    This confusing result becomes a challenge to the hierarchical growth model 
    of massive galaxies. 
    On the observational side, both the depth of the images and the photometric 
    method contribute to this problem. 
    The steep inner \mden{} profiles, extremely extended stellar envelopes, and other
    structural details make it very difficult to accurately define and measure the 
    \mstar{} and $R_{\mathrm{e}}$ of massive ETGs (e.g. \addref{}).

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}[bt]
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
        \caption{
            Left: example of the 1-D surface brightness and ellipticity profile 
            for a massive galaxy at $z=0.23$ in the $i$-band using \texttt{Ellipse}. 
            In this work, we always show the radial profile using a $R^{1/4}$ scaling 
            on the x-axis. 
            By using this scale, the de Vaucouleurs profile will appear as a straight 
            line on this figure. 
            The dash-line shows the surface brightness profile after correcting the 
            background. 
            We also plot the relative brightness profile of the PSF model normalized 
            at the central surface brightness of the galaxy to highlight the region 
            affected by seeing. 
            The grey shaded region highlights the region most affect by seeing 
            ($r<3$ kpc).
            On the top panel, the dash line shows the ellipticity used for the final 
            isophote. 
            Right: the masked $i$-band image of this galaxy with the isophotes 
            extracted by \texttt{Ellipse}. 
            The thick dotted line highlights the isophote with 
            $\mu_{i}\sim 28.5$~\sb.
            }
        \label{fig:ellipse}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[bt!]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_smf_new}
      \caption{
          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
          On average, \mcmodel{} underestimates the total stellar mass of massive 
          galaxies by 0.1 dex while the difference can exceed 0.2 dex in some cases.
          Vertical histograms indicate the mass difference for galaxies with
          $11.6<$\logmtot{}$<11.9$. 
          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
          function. 
          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
          of the total luminosity whereas solid lines correspond to the SMF computed
          using the total luminosity from our 1-D profile. 
          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
          living in halos larger than $\log (M_{200m}/M_{\odot}) > 14.2$ (red lines).
          }
      \label{fig:smf1}
  \end{figure*}

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[bt!]
      \centering 
      \includegraphics[width=\textwidth]{fig/average_mass_profiles_fsps1_A}
      \caption{
          \textbf{Left}: Median \mden{} profiles of galaxies in different \mtot{} bins:
      	  [11.4, 11.6] (short-dashed line), [11.6, 11.8] (solid line), and 
      	  [11.8, 12.0] (long-dashed line). 
      	  Here we combine the \rbcg{} and \nbcg{} samples, and we also show a random 
      	  subset of individual profiles in the background.
      	  The shaded region highlights the region that could be affected by PSF.
          Two vertical lines label the radius of 10 kpc (thin, dotted line) and
          100 kpc (thick, dash line). ~~~ 
          \textbf{Right}: comparison between the average \mden{} profiles with the ones 
          from previous observations and simulations, including: 
          1) average profile of massive elliptical galaxies at $z\sim 0$ from 
          \citet[][Cyan, solid]{Huang2013a}; 
          2) average profile of massive galaxies at $0.25 \leq z < 0.50$ observed by 
          \textit{HST} from \citet[][Red, long-dashed]{Patel2013} ;
          3) average radial stellar distributions in massive halos using simulation and 
          particle tagging method (\citealt{Cooper13}; Purple, short-dashed).
          }
      \label{fig:avg_prof}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[t!]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
      \caption{
          Comparison of the \mden{} profiles for \mtot{}-matched 
          ($11.6<$\logmtot{}$<11.9$) and \minn{}-matched ($11.2<$\logminn{}$<11.6$) 
          samples of \rbcg{} (orange to red) and \nbcg{} (grey to black) galaxies.~~
          \textbf{Left} shows the results for the \mtot{}-matched samples.
          For details of the matching process, please see Appendix~\ref{app:match}.  
          On its upper panel, we show the \mden{} profile of each galaxy using very light 
          color in the background.  
          We highlight the median profile and its corresponding uncertainties using thick 
          solid line with darker color and shaded region. 
          Other formats are the same with Fig~\ref{fig:avg_prof}.
          Meanwhile, we highlight the difference between the median profiles and its 
          uncertainty on the bottom panel (brown solid line and shaded region).
          To test the significance of the differential profile, we perform statistical
          tests by comparing the median profiles of two random groups that are drawn 
          from the mixed sample, and have the same sizes with the matched \rbcg{} and
          \nbcg{} ones.
          Repeating this process many times, the median of these random differential 
          profiles (black solid line), the 1-$\sigma$ (dark-grey shaded region) and 
          3-$\sigma$ (light-grey shaded region) uncertainties are shown on the bottom 
          panel as well. 
          A darker vertical dash-line highlights the 100 kpc radius.~~
          \textbf{Right} shows the results for the \minn{}-matched samples. 
          The format is exactly the same with the left one, except that the darker 
          vertical dash-line now highlights the 10 kpc radius.
          }
      \label{fig:prof_1} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    As mentioned above, different methods lead to different estimates of ``total'' 
    \mstar{} and impacts important statistics like the stellar mass function 
    (e.g. \addref{}).
    We highlight this in the left panel of Fig~\ref{fig:smf1} by plotting 
    the \mtot{} from 1-D analysis with the differences between \mtot{} and \mcmodel{}.
    Apparently, our careful 1-D approach recovers more flux in massive galaxies 
    than the \texttt{cModel} method. 
    More importantly, the average difference steadily increases with \mtot{}. 
    At \logms$>11.5$, the difference is often larger than 0.2 dex.  
    This difference relates to the intrinsic limitation of the \texttt{cModel} 
    method and also reflects the fact that more massive ETGs tend to have more 
    extended stellar mass distributions (e.g.\ \addref{}).

    Such mass-dependent difference will clearly result in difference of the SMF, 
    especially at the very high-mass end where the slope is quite uncertain under
    current constraints (e.g. \ \addref{}).
    Although the careful evaluation of the SMF is beyond the scope of this work, 
    we still highlight the impacts of different definitions of ``total \mstar{}''
    on the volume density distributions of both samples (Fig~\ref{fig:smf1}, 
    right panel).  
    Generally speaking, the use of \mtot{} from 1-D analysis instead of the
    \mcmodel{} shifts the distributions toward the higher-mass end, and slightly 
    modifies the slope.
    This impact is more obvious for the \rbcg{} samples.
    For studies about the SMF or other aspects of galaxy evolution based on 
    \cmodel{}-like photometry or shallower images, these impacts should be 
    taken into consideration.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[t!]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_discussion_2}
      \caption{
          Comparisons of the radial profiles of ellipticity and optical colors 
      	  for \mtot{}-matched (\textbf{left figure}) and \minn{}-matched 
      	  (\textbf{right figure}) of \rbcg{} (orange-red) and \nbcg{} (grey-black) samples. 
          The formats are very similar to the figure for \mden{} profile 
          (e.g. right figure of Fig~\ref{fig:prof_1}). 
          On each side, from top to bottom, we show the elliptical profile, and the 
          color profile using $g-r$ and $g-i$ color. 
          Since the individual profile of these properties has very large uncertain in the 
          outskirt, we block the region at large radii where we think the median profiles 
          are still unreliable using a dark, shaded box.
          We also compare these results with previous results based on SDSS images. 
          They are: 
          1) Ellipticity profile of the stacked image of a large sample of red galaxies at 
          $z\sim 0.4$ from \citet{Tal2011} with PSF correction 
          (solid blue line on top panel); 
          2) Ellipticity and $g-r$ color profiles from stacking analysis of nearby massive 
          galaxies with high concentration index ($C>2.6$) in \citet[][blue dash lines 
          on the top and middle panels]{DSouza2014}; 
          3) average $g-r$ and $g-i$ color profiles for a large sample of nearby 
          elliptical galaxies in \citet[][blue, solid lines on the middle and bottom 
          panels]{LaBarbera2010}.
          }
      \label{fig:ell_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

\acknowledgements

@@

\bibliography{redbcg}
